Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
Minor comment from discussion

@@

\TODO{We have to also cite the paper by Konstantinos, Caleb, Rajeev,
  etc since they also try to do semantics preserving optimizations on
  dataflow graphs}

>>>>

\kk{exoume ena semantic model to opoio mporei na xrhsimopoiithei gia
  na ginoun formally proven claims gia to equivalence preservation twn
  optimizations etc.}

@@

%% \TODO{We have to also cite the paper by Konstantinos, Caleb, Rajeev,
%%   etc since they also try to do semantics preserving optimizations on
%%   dataflow graphs}
